conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-01 paper/paper.Rmd
Updated introduction

These social contact surveys exist for a few countries. As an example, the "POLYMOD" study by @mossong2008 covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008]. However, what do we do when we want to (?)look at/estimate contact rates in other countries that have not been measured? We can use this existing data to help us project to countries or places that do not have empirical survey data. These are called "synthetic contact matrices". A popular approach by @prem2017 projected from the POLYMOD study to 152 countries. This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].

However not all countries were included in this list from @prem2021, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country. One limitation of this is that the predictions were not provided at smaller grained regions. This might be important, if for example, a public health group needed to make predictions for specific areas. It was challenging to apply the methodology used by Prem et al, as while their analysis code was provided, it was not designed for reuse.

>>>>

These social contact surveys exist for a few countries. As an example, the "POLYMOD" study by @mossong2008 covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008]. However, what do we do when we want to (?)look at/estimate contact rates in other countries that have not been measured? We can use this existing data to help us project to countries or places that do not have empirical contact survey data. These are called "synthetic contact matrices". A popular approach by @prem2017 projected contact rates from the POLYMOD study to 152 countries. This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].

However, there were major limitations with the methods in @prem2021. First, not all countries were included in their analyses. Second, some of the synthetic contact matrices did not have enough granularity; they covered a large area, such as "urban" or "rural" for a given country. This is disadvantegous as public health groups might need to make predictions for more fine-grained areas within a country, such as a district or municipality. Third, the methodology used by Prem et al. was challenging to reuse in other contexts. Prem et al. provided the code used for their analysis, but that code was not designed for replicability and user-defined inputs.
